$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Changed subsections to sections

The structure of this paper is as follows.  In section \ref{sec:model}
we review the models we consider.  In section \ref{sec:ewsb} we
specify the EWSB conditions of the models, with particular focus on
how the $Z^\prime$ mass influences the prediction of $M_Z$.  Then in
section \ref{sec:tuning} we introduce our fine tuning measure and our
approach to evaluating it to obtain the individual sensitivities.  The
numerical procedure we use to obtain our results is given in
\ref{subsec:numericalprocedure} and then the results are specified in
section \ref{sec:results}.

@@

\subsection{\label{subsec:tuningmeasure}The Fine Tuning Measure}

@@

\subsection{\label{subsec:numericalprocedure}Numerical Procedure}

>>>>

The structure of this paper is as follows.  In section \ref{sec:model}
we review the models we consider.  In section \ref{sec:ewsb} we
specify the EWSB conditions of the models, with particular focus on
how the $Z^\prime$ mass influences the prediction of $M_Z$.  Then in
section \ref{sec:tuning} we introduce our fine tuning measure and our
approach to evaluating it to obtain the individual sensitivities.  The
numerical procedure we use to obtain our results is given in
\ref{sec:numericalprocedure} and then the results are specified in
section \ref{sec:results}.

@@

\section{\label{sec:tuningmeasure}The Fine Tuning Measure}

@@

\section{\label{sec:numericalprocedure}Numerical Procedure}
